Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-03-19 paper.tex
Fix fig names so document can compile

\draft % marks overfull lines with a black rule on the right

@@

    \includegraphics[clip, trim=0 1in 0 1in, width=0.8\textwidth]{BR-CFD_CAD}

@@

    \includegraphics[width=0.8\textwidth]{BR-CFD_2D_mesh}

@@

    \includegraphics[width=0.7\textwidth]{BR-CFD_2D_blade_mesh_closeup}

@@

    \includegraphics[width=0.9\textwidth]{BR-CFD_verification}

@@

    \includegraphics[width=0.95\textwidth]{BR-CFD_perf_bar_chart}

@@

    \includegraphics[width=0.75\textwidth]{BR-CFD_2D_vorticity_SA_964}

@@

    \includegraphics[width=0.75\textwidth]{BR-CFD_3D_vorticity_SA_964_10-threshold}

@@

    \includegraphics[width=0.95\textwidth]{BR-CFD_profiles}

@@

        \includegraphics[clip, trim=0 0.1in 0.3in 0.2in,
        width=0.72\textwidth]{RVAT-Re-dep_meancontquiv_10}

@@

        \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{BR-CFD_meancontquiv_kOmegaSST}

@@

        \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{BR-CFD_meancontquiv_SpalartAllmaras}

@@

        \includegraphics[width=0.95\textwidth]{RVAT-Re-dep_k_contours_10}

@@

        \includegraphics[width=0.95\textwidth]{BR-CFD_kcont_kOmegaSST}

@@

        \includegraphics[width=0.95\textwidth]{BR-CFD_kcont_SpalartAllmaras}

@@

    \includegraphics[width=0.9\textwidth]{BR-CFD_mom_bar_graph}

>>>>

\draft % marks overfull lines with a black rule on the right
\usepackage{graphicx}
\graphicspath{{figures/}}

% Footnotes in tables
\usepackage{tablefootnote}

@@

    \includegraphics[clip, trim=0 1in 0 1in, width=0.8\textwidth]{CAD}

@@

    \includegraphics[width=0.8\textwidth]{2D_mesh}

@@

    \includegraphics[width=0.7\textwidth]{2D_blade_mesh_closeup}

@@

    \includegraphics[width=0.9\textwidth]{verification}

@@

    \includegraphics[width=0.95\textwidth]{perf_bar_chart}

@@

    \includegraphics[width=0.75\textwidth]{2D_vorticity_SA_964}

@@

    \includegraphics[width=0.75\textwidth]{3D_vorticity_SA_964_10-threshold}

@@

    \includegraphics[width=0.95\textwidth]{profiles}

@@

        \includegraphics[clip, trim=0 0.1in 0.3in 0.2in,
        width=0.72\textwidth]{meancontquiv_exp}

@@

        \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{meancontquiv_kOmegaSST}

@@

        \includegraphics[clip, trim=0 0.2in 0 0.15in,
        width=0.8\textwidth]{meancontquiv_SpalartAllmaras}

@@

        \includegraphics[width=0.95\textwidth]{kcont_exp}

@@

        \includegraphics[width=0.95\textwidth]{kcont_kOmegaSST}

@@

        \includegraphics[width=0.95\textwidth]{kcont_SpalartAllmaras}

@@

    \includegraphics[width=0.9\textwidth]{mom_bar_graph}
